Mines Accident Prediction

### 2017-03-04 A New Hope/Catherine_Analysis.Rmd
Update Catherine_Analysis.Rmd

all.quarter.level.accidents <- accidents %>% group_by(mine_id, cal_qtr, cal_yr)%>% 
                                            summarize(base = sum(days_lost, na.rm = T) + sum(days_restrict, na.rm = T))
all_accident_rollover <- roll_over(accidents,
                                   all.quarter.level.accidents,
                                   longest.period,
                                   1984,
                                   2016)
all_accident_rollover

all_violation_rollover <- roll_over(accidents,
                                   quarter.level.violations,
                                   longest.period,
                                   1984,
                                   2016)
all_violation_rollover

@@

#remove start year
for (x in unique(all_accident_rollover$mine_id)){
  temp <- all_accident_violation_rollover %>% filter(mine_id==x)
  i <- 1
  while( sum(temp[i,3:11]) == 0){
    i = i+1
  }
  if(i != 1){
    print(x)
    print(i)
    temp <- temp[-1:i,]
  }
}

  #remove end year
for (mine_id in unique(all_accident_rollover$mine_id)){
  temp <- all_accident_violation_rollover %>% filter(mine_id==x)
  i <- nrow(temp)
  while( sum(temp[i,3:11]) == 0){
    i = i-1
  }
  if(i != nrow(temp)){
    print(x)
    print(i)
    temp <- temp[-i:nrow(temp),]
  }
}

>>>>

accidents[which(accidents$inj_degr_desc == "FATALITY"), "days_lost"] <- 300
all.quarter.level.accidents <- accidents %>% group_by(mine_id, cal_qtr, cal_yr)%>% 
                                            summarize(base = sum(days_lost, na.rm = T) + sum(days_restrict, na.rm = T))
all_accident_rollover <- roll_over(accidents,
                                   all.quarter.level.accidents,
                                   longest.period,
                                   2000,
                                   2015)
all_accident_rollover

all_violation_rollover <- roll_over(accidents,
                                   quarter.level.violations,
                                   longest.period,
                                   2000,
                                   2015)
all_violation_rollover

@@

all_accident_violation_cleaned <- data.frame()
counter <- 1
for (x in unique(all_accident_rollover$mine_id)){
  print(counter)
  counter = counter +1
  temp <- all_accident_violation_rollover %>% filter(mine_id==x)
  i <- 1
  while( sum(temp[i,4:11],na.rm = TRUE) == 0){
    i = i+1
  }
  if(i != 1){
    temp <- temp[-c(1:15),]
  }

  i <- nrow(temp)
  while( sum(temp[i,4:11]) == 0){
    i = i-1
  }
  if(i != nrow(temp)){
    temp <- temp[-c(nrow(temp)-i:nrow(temp)),]
  }
  all_accident_violation_cleaned <- rbind(all_accident_violation_cleaned,temp)
}
all_accident_violation_cleaned
```
